---
title: "post 1"
categories: [cat1, cat2, cat3]
title-block-banner: true
toc: true
toc-title: Table of contents
toc-location: left
execute:
  echo: true
  message: true
  warning: true  
---

a number of additional axe-core warnings go off here.

## Section 1

```{r}
text <- '<?xml version="1.0" encoding="UTF-8"?>
<gpx creator="StravaGPX Android" version="1.1" xmlns="http://www.topografix.com/GPX/1/1" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance" xsi:schemaLocation="http://www.topografix.com/GPX/1/1 http://www.topografix.com/GPX/1/1/gpx.xsd">
'

cat(text)
```


## Section 2

```{r}
library(profvis)

f <- function() {
  Sys.sleep(0.2)
  return(1 + 1)
}

profvis(f())
```

### section 3

::: {.callout-warning collapse="true"}
## Small variations in scores will have minimal impact on lottery outcomes

In practice, you probably want scores to be on a multiplicative scale for them to impact lottery outcomes -- i.e., if you want a certain entrant to be more likely to win, their score should be orders of magnitude higher than typical scores.
:::

### section 4

::: {.callout-warning collapse="true"}
## Large scores can lead to unexpected behavior

You will likely also want to enforce that $\frac{s_i^T}{\sum_{i \in U} s_i^t} < \frac{1}{K_t}$, because otherwise the scores imply that node $i$ should be allocated more than one winning seat. From a pragmatic perspective, all the code still runs fine, but this can have surprising impacts on cumulative unfairness over time, because entrant $i$ can win the lottery and the system will still say they haven't earned all the winning seats they are entitled, which impacts future lotteries.
:::

::: {.callout-note collapse="true"}
## Quotas

It is theoretically possible to require that lottery outcomes satisfy hard quotas on groups (for instance, when you want lottery winners to reflect an underlying population), but this becomes a much more technically challenging problem. The difficulty is that it is NP-hard to find any subset of candidates that even satisfy the quotas, meaning that simple sampling procedures cannot be guaranteed to satisfy the quotas [@flanigan2021a]. Bailey notes that the approach in @flanigan2021a can likely be extended to the repeated lottery setting, but this is far above my pay grade.
:::


```{r}
#| code-fold: true
g <- function() {
  Sys.sleep(0.2)
  return(1 + 1)
}
```

## Appendix {.appendix}

```{r}
#| code-fold: true
g <- function() {
  Sys.sleep(0.2)
  return(1 + 1)
}
```